% !TEX TS?program = pdflatexmk
\documentclass[]{mbcv}

\usepackage{xcolor}
\usepackage{marvosym}
\usepackage{array}
\usepackage{hyperref}
\pagenumbering{gobble}
\usepackage{afterpage}
\usepackage{ragged2e}
\usepackage{fontawesome5}
\definecolor{background}{HTML}{e1e1e1} 
\definecolor{border}{HTML}{e1e1e1} 
\usepackage[backend = biber, sorting=ydnt, maxbibnames=99]{biblatex}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
%\renewcommand{\refname}{Publications}

\newcommand{\detailsvspace}{5pt}

\begin{document}

\namesection{Matthew David Blackledge}{PhD, MSc, BSc}

\noindent\fcolorbox{border}{background}{%
\begin{minipage}[t][0.9\textheight]{0.3\textwidth}
\section{Personal Details}
\vspace{\detailsvspace}
 \Writinghand\hspace*{3pt}  17 Elmhurst Lodge\\
\hspace*{12pt} Christchurch Park\\
\hspace*{12pt} Sutton, SM2 5TY\\
\hspace*{12pt} United Kingdom

\vspace*{5pt}

\Letter\hspace*{3pt}   \href{matthew.blackledge@icr.ac.uk}{matthew.blackledge@icr.ac.uk}

\vspace*{5pt}

\Telefon\hspace*{3pt}  +44 (0)7581 016 932

\vspace*{5pt}

\Mundus\hspace*{6pt}
\href{https://sites.google.com/view/blackledgelab}{blackledgeimaging.co.uk}

\vspace*{5pt}

\faLinkedin\hspace*{4pt} \href{https://www.linkedin.com/in/mdblackledge/}{linkedin.com/in/mdblackledge}

\vspace*{5pt}

\faGithub\hspace*{3pt} \href{https://github.com/mdblackledge}{mdblackledge}

\vspace*{\detailsvspace}

\sectionsep
\section{Education}
\vspace{\detailsvspace}
\descript{Institute of \newline Cancer Research}
\location{PhD in Medical Physics:} 
Assessing response in bone metastases using Diffusion-\newline Weighted MRI
\newline
2007-2011
\sectionsep

\descript{Surrey University}
\location{MSc in Medical Physics}
2006-2007 (Distiction)
\sectionsep

\descript{Imperial College}
\location{BSc in Physics}
2003-2006

\vspace*{\detailsvspace}

\sectionsep
\section{Programming}
\vspace{\detailsvspace}
\location{Languages}
 C \textbullet{}  C++ \textbullet{} Objective-C  \\
Python \textbullet{} Python-C API   \\
 \LaTeX \textbullet{} R \textbullet{} HTML \textbullet{} IDL\\
 gRPC \textbullet{} Markdown  \\
 
\vspace{5pt}
\location{Administrative Tools}
Unix \textbullet{} Conda \textbullet{} Jupyter  \\
Git \textbullet{} Confluence \textbullet{} Jira \\

\vspace{5pt}
\location{Machine Learning}
TensorFlow \textbullet{} Keras \textbullet{} PyTorch  \\
Scikit-Learn \textbullet{} SimpleITK

\vspace*{\detailsvspace}
\sectionsep
\section{Languages}
English \textbullet{} Polish

\vspace*{30pt}

\end{minipage}}%
\hfill
\begin{minipage}[t]{0.65\textwidth}

\section{Professional Experience}
\location{Team Leader of Computational Imaging | 2019-present \newline Institute of Cancer Research}
Lead a team of postdoctoral fellows and PhD/MSc students, combining quantitative MRI and CT imaging with innovative image processing and artificial intelligence to solve clinical problems in oncology. Focus on prostate, breast, head/neck, gynaecological, and connective tissue cancers. Core ambitions to:
 
\vspace*{15pt}
\begin{tightemize}
\item Promote personalised risk stratification with \textbf{deep-learning} and \textbf{radiomics} by discovering new imaging biomarkers of response and prognosis.
\item Reduce clinician burden using \textbf{domain-adaptation AI} for automatic segmentation of tumours and organs at risk during radiotherapy planning.
\item Establish new biomarkers of heterogeneous tumour response through \textbf{bayesian and mathematical modelling} of quantitative MRI.
\item Improve the patient experience and departmental capacity of quantitative MRI by innovating AI-accelerated \textbf{image reconstruction}.
\item Decipher the link between tumour biology and quantitative MRI using \textbf{computational histopathology} and super-resolution ultrasound.
\end{tightemize}

\sectionsep

\location{Director | 2021-2024, Diafora Medical Ltd.}
Co-founded Diafora Medical Ltd. to commercialise my Artificial Intelligence algorithm for accelerating acquisition of clinical Diffusion-Weighted MRI scans. Responsibilities include overall strategy of company direction, authorship of patents, leading clinical trial development, and raising funds to develop the invented techniques.

\sectionsep

\location{Postdoctoral Research Fellow | 2011-2019, Institute of Cancer Research}
Won multiple rounds of competitive funding to develop automated segmentation of total body disease from whole-body MRI, and turn the technology into an approved medical device. Achievements include:

\vspace*{5pt}
\begin{tightemize}
\item Leading \textbf{whole-body MRI} protocol development within the department and promoting its use within multi-center clinical trials. 
\item Developing novel AI-based \textbf{image segmentation} for whole-body MRI and PET/CT in patients with advanced prostate cancer and lymphoma.
\item Steering development of \textbf{regulatory approved software} for automatic assessment of patients with metastatic cancer using whole-body MRI.
\item Pioneering in-silico approaches to correlate quantitative MRI with histopathology in preclinical prostate cancer models.
\item Innovating \textbf{open-source software} (pyOsiriX) to accelerate prototyping of medical imaging research tools.

\end{tightemize}

\sectionsep

\location{Consultancy Positions}
\vspace*{5pt}
\textbf{Nomela (2021-present):} Head of AI Development,  leading implementation of clinical teleradiology for diagnosis of skin cancer.
\newline
\newline
\textbf{Bayer AG (2019-present):} Lead MRI protocol development for multi-center testing of novel pharmaceuticals, including development of bespoke image analysis software.


\end{minipage}

\newpage
\section{Leadership and Mentoring}
\vspace*{10pt}
\begin{tightemize}
\item Experience of leading small-medium research teams in image-processing, MRI physics, and artificial intelligence; currently six PhD students and three postdoctoral fellows (one student has recently defended their thesis).
\item Mentored seven summer studentships/interns in the development of image processing for MRI.
\item Management of grant funds and resources, both within personal fellowships and project awards.
\item Chair of the Career Development Faculty committee at the Institute of Cancer Research, London (2019-present).
\item Joint chair of the Vibrant Research Culture Working Group at the Institute of Cancer Research, London (2021-present). 
\item Lead a number of \textbf{clinical trials}, including development of overall research methodology, \textbf{statistical analysis} plans, power calculations, imaging protocol manuals, and patient information sheets. 

\end{tightemize}
\sectionsep

\section{Scientific Outreach and Teaching}
\vspace*{10pt}
\begin{tightemize}
\item Invited key speaker at prominent international and national scientific meetings.
\item Principle lecturer at the annual mathematics and imaging course at the Royal Marsden Hospital (RMH) (interactive slides: \href{https://github.com/mattblackledge/mathematicsofimaging}{https://github.com/mattblackledge/mathematicsofimaging}).
\item Run and deliver courses on the use of \LaTeX\  for graduate students within the Institute of Cancer Research (ICR). 
\item Invited member of the scientific editorial board for European Radiology.
\item Regular peer-reviewer for a number of relevant journals (including European Radiology, Magnetic Resonance in Medicine, and Computers in Biology and Medicine).
\item External examiner of the digital health MSc course at St Andrews University.
\item Deliver annual lecture series on Diffusion Weighted MRI and Imaging Biomarkers at the Higher Specialist Scientist Training programme (University of Manchester).
\item Invited member of the ESMRMB congress planning committee in 2020 and 2021.
\item Deliver lectures to patients and public groups, both informative and as part of fund-raising campaigns. 
\end{tightemize}
\sectionsep


\section{Research Collaborations}
\vspace*{10pt}
\begin{tightemize}
\item Develop optimised MRI protocols at institutions across the UK to support multi-centre clinical imaging trials.
\item Member of MY-RADS working group, acting as leading MR-physicist to develop imaging recommendations that promote standardisation of acquisition and reporting of whole-body MRI in myeloma.
\item Established a collaboration with Norwegian University of Science and Technology (NTNU) to investigate the use of advanced histopathological analysis for MRI biomarker validation.
\item Jointly established a collaboration with an industrial partner (Mint Medical GmbH) to support software development to a commercial standard.
\item Initiated a collaboration between six UK institutions to perform an AI project in prediction of lung cancer occurence and won competitive funding to complete the project.
\item Core member of the multi-national CRUK Sarcoma Accelerator project, leading on development of AI and radiomics arms of the project studies.
\end{tightemize}

\section{Awards}
\vspace*{10pt}
\begin{tightemize}
\item Commended for Innovation Award, Institute of Cancer Research (2022)
\item First prize for presentation to the MR of Cancer Study Group at the annual meeting of the International Society for Magnetic Resonance in Medicine (2017). 
\item Sylvia Lawler prize from the Royal Society of Medicine for development of innovative imaging methodologies for quantification response heterogeneity from whole-body MRI (2013).
\item Summa cum laude awards at the ISMRM annual meetings (2013 and 2016).
\item Certificate of merit award at the annual meeting of ESMRMB (2008).
\end{tightemize}

\newpage

\section{Grant Funding}
\begin{table}[htp]
\begin{center}
\begin{tabular}{|P{0.15\linewidth}|P{0.5\linewidth}|P{0.1\linewidth}|P{0.15\linewidth}|}
\hline
\textbf{Name of funding organisation} & \textbf{Project Title} & \textbf{Amount awarded} & \textbf{Role} \\
\hline
Medical Research Council (MRC)  & AI-assisted contour generation for enhanced pelvic radiotherapy planning on the MR-linac & £49,288 & Principle Investigator \\
\hline
National Institute of Health Research (NIHR) Biomedical Research Center & Deciphering heterogeneity in treatment-induced changes of limb sarcomas through dynamic habitat mapping & £27,553 & Principle Investigator \\
\hline
National Institute of Health Research (NIHR) Biomedical Research Center & Improving imaging in mesothelioma	& £23,404 & Co-Investigator \\
\hline
National Institute of Health Research (NIHR) Biomedical Research Center & Developing and testing radiomics-derived models for early cancer detection on MRI in men with genetic high-risk of developing prostate cancer & £38,838 & Co-Investigator \\
\hline
National Institute of Health Research (NIHR) & Real-world testing of software for measuring bone disease on whole-body MRI in patients with prostate cancer and myeloma	& £1,955,730 & Co-Investigator \\
\hline
NIHR Biomedical Research Centre & PhD studentship: AI for improved patient outcome prediction in brain metastasis &	£149,770	& Principle Investigator\\
\hline
MedTech SuperConnector & Next generation whole-body imaging for painful metastatic disease & £88,740 & Principle Investigator \\
\hline
CRUK Centre for Convergence Science & PhD studentship: Combined functional MRI and super-resolution ultrasound for non-invasive monitoring of tumour blood delivery during radiotherapy of breast cancer & £149,770 & Co-Principal Investigator \\
\hline
CRUK Centre for Convergence Science & Application of novel 3D super-resolution ultrasound imaging for radiotherapy response assessment in breast tumours & £29,954 & Co-Principal Investigator \\
\hline
Global Challenges Research Fund & CCR5115 KORTUC phase II - Randomised phase II trial testing efficacy of intra-tumoural hydrogen peroxide as a radiation sensitiser in patients with locally advanced/recurrent breast cancer & £ 79,930 & Co-investigator \\
\hline
Cancer Research UK & Improving neoadjuvant therapy in high-risk sarcoma & £1,493,584 & Co-Investigator\\
\hline
Sarcoma UK & Using MRI for response assessment of soft-tissue sarcoma to pre-operative radiotherapy & £24,490 & Principle Investigator \\
\hline
Institute of Cancer Research & Career Development Faculty start-up package & £950,000 & Principle Investigator \\
\hline
NIHR & Evaluating treatment response of whole-body metastases with multi-modality imaging & £242,628 & Principle Investigator \\
\hline
\end{tabular}
\end{center}
\end{table}
 \newpage

\begin{table}[htp]
\begin{center}
\begin{tabular}{|P{0.15\linewidth}|P{0.5\linewidth}|P{0.1\linewidth}|P{0.15\linewidth}|}
\hline
\textbf{Name of funding organisation} & \textbf{Project Title} & \textbf{Amount awarded} & \textbf{Role} \\
\hline
Cancer Research UK & Predicting the location of lung nodule occurrence from low-dose CT using convolutional time-to-event networks (X-Net) & £99,470 & Principle Investigator \\
\hline
David \& Ruth Lewis Family Charitable Trust & PhD studentship: Developing methods for automated response characterisation of soft-tissue sarcoma following pre-operative radiotherapy. How artificial intelligence can improve our knowledge of heterogeneous change. & £149,770 & Principal Investigator \\
\hline
NIHR & Advanced computer diagnostics for whole body magnetic resonance imaging to improve management of patients with metastatic bone cancer & £1,201,674 & Co-Investigator \\
\hline
\end{tabular}
\end{center}
\end{table}

% Papers
\begin{refsection}[papers.bib]
\nocite{*}
\section{Publications}
\vspace*{10pt}
\printbibliography[heading=none]
\end{refsection}

% Preprints
\begin{refsection}[preprints.bib]
\nocite{*}
\section{Pre-prints}
\vspace*{10pt}
\printbibliography[heading=none]
\end{refsection}

% Patents
\begin{refsection}[patents.bib]
\nocite{*}
\section{Patents}
\vspace*{10pt}
\printbibliography[heading=none]
\end{refsection}

% Invited talks
\section{Invited Talks}
\begin{itemize}
\item ESMO Sarcoma and Rare Cancer Congress, "Radiomics in sarcomas: Where do we stand?", 2023 (Lugano, Switzerland)
\item Annual Conference of the Association for Radiation Research, "Accelerating acquisition and analysis of quantitative oncological imaging with AI", 2022 (Francis Crick Institute, UK)
\item ESMO Sarcoma and GIST Symposium, "Radiomics for sarcomas", 2022 (online).
\item "Computational Imaging", 2022 (Sanjay Gandhi Postgraduate Institute Of Medical Sciences, India)
\item ICIS, The Wizardry of Artificial Intelligence 2.0, "Disease segmentation", 2021 (online)
\item The ICR Discovery Club, "Improving imaging with artificial intelligence", 2021 (online)
\item Sarcoma Webinar Series, "Artificial Intelligence and quantitative imaging: a new paradigm for sarcoma response assessment?", 2020 (online)
\item EORTC Patient Days, "Real-World Data and Artificial Intelligence in cancer research: fundamentals", 2020 (Brussels, Belgium)
\item EORTC Patient Days, "Oxford debate: Real-World Data, the end of prospective clinical
trials? ", 2020 (Brussels, Belgium)
\item "Clinical Computational Imaging: Perspectives in Oncology", 2020 (St Andrews University, UK)
\item "Quantitative imaging for detecting cancer and monitoring tumour response: How computational science can improve patient outcome", 2019 (Cambridge University, UK)
\item NIHR Patient, carer, family and friends event, "Machine learning – pioneering imaging", 2019 (London, UK).
\item IPEM Conference on Diffusion MRI, "Mathematical Tools in Whole-Body Diffusion-Weighted MR-Imaging of Metastatic Cancer", 2017 (Society of Chemical Industry, UK)
\item "Mathematical tools in DW-MRI: Probing the microscopic and macroscopic worlds in cancer", 2015 (Norwegian University of Science and Technology, Norway)
\item Centre for Mathematical Imaging Techniques Workshop, "Mathematical tools in DW-MRI: Probing the microscopic and macroscopic worlds in cancer", 2015 (Liverpool University, UK)
\end{itemize}

% Abstracts
\begin{refsection}[abstracts.bib]
\nocite{*}
\section{International Conferences}
\vspace*{10pt}
\printbibliography[heading=none]
\end{refsection}

\clearpage
\restoregeometry

\end{document}